% !TEX root = ..\main.tex

\KeyWords{Coffee consumption, Machine learning, Purchase data, Consumption pattern, Types of coffee, Habits per person.}
\centeredchapterstyle
\begin{abstract}
    \noindent\textbf{Contextualization}: Coffee is one of the world's most popular beverages, enjoyed by millions of people for its flavor, aroma, and stimulating effect. Coffee consumption can offer various health benefits, such as reducing the risk of chronic diseases and improving cognitive function. However, excessive consumption can lead to adverse effects, such as insomnia, anxiety, and digestive problems. \textbf{Objetive}: This study aimed to analyze the coffee consumption pattern in a specific population using data collected from a database that records each purchase made. The exploratory analysis aimed to identify trends, habits, and characteristics of consumption in order to provide relevant information to better understand consumer behavior and assist in decision-making related to the coffee market. \textbf{Method}: 
The research was based on an exploratory data analysis of purchases recorded in a coffee purchase database. The data was organized and processed to identify relevant variables, such as coffee type, quantity purchased, purchase frequency, and purchase time. Descriptive statistical techniques were then applied to describe the consumer profile and characterize the consumption pattern. \textbf{Results}: Exploratory Analysis Findings:

The exploratory data analysis revealed several relevant insights into coffee consumption patterns among the studied population. Key findings include:

1. Most Popular Coffee Types:

Identify the specific coffee types that were most frequently purchased.

2. Average Daily Coffee Consumption:

Determine the average amount of coffee consumed per day by individuals.

3. Purchase Frequency:

Analyze the average frequency of coffee purchases among consumers.

4. Peak Consumption Times:

Identify the times of day when coffee consumption is at its highest.

5. Consumer Profile:

Describe the demographic and behavioral characteristics of coffee consumers. \textbf{Conclusion}: Implications of Coffee Consumption Analysis:

The exploratory analysis of coffee consumption provides valuable insights into consumer behavior and market trends. These findings can be utilized by companies in the coffee industry to:
\end{abstract}
